### 2019-05-09 2-Chapters/5-Chapter/chapter5.tex
I'm happy about the modifications for Chapter 5:
- no proof for lower-bound
- less figures
- shorter Appendix
- few more details in a proof
- less clutter in some equations

In this Chapter~\ref{chapter:5}, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We start by reviewing previous works on multi-player MAB models, which all considered the easier case of \emph{sensing feedback}.
For this first model, we present two algorithms, \RandTopM{} and \MCTopM, based on the combination of an efficient MAB index policy (we chose \klUCB) and a smart orthogonalization procedure, based on a random hoping procedure called Musical Chair.
Like in previous works, we consider the centralized system regret (multi-player regret).
We start by showing an improved asymptotical regret lower-bound for any algorithm of a certain class, including previous solutions such as \rhoRand{} and our two solutions.
We then analyze our \MCTopM{} algorithm and we show that its regret upper-bound is logarithmic and order-optimal, improving over the previous state-of-the-art.
%  with a regret bounded by $\bigO{\log(T)}$ for a game at horizon $T$.
We also present extensive numerical simulations that show that our proposal outperforms all previous solutions and is much more efficient in this easier model of sensing feedback with a fixed and known number of players $M \leq K$ accessing $K$ channels.

@@

Finally, we review other extensions of our model, and give a overview of the current state-of-the-art.
For some extensions, we discuss how to adapt our proposal and illustrate the empirical performances of such modification of \MCTopM-\klUCB{}, leaving theoretical analyses as future works.

@@

\newpage  % WARNING
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\section{Literature review of many extensions of our models}
\label{sec:5:literatureReviewOtherModels}
% ----------------------------------------------------------------------------

@@

Many extensions of the simpler model of multi-player bandits have been considered.
The number of players $M$ can be fixed but initially unknown to the players, the sensing information can be absent (like our \modeltrois{} presented above), there could be communications between players (happening at each time step or only occasionally), or $M$ could evolve over time to model the possibility of arrivals or departures of players (\ie, connexions and disconnections of devices in a wireless networks).
Also inspired by real-world wireless networks, the arm means may vary among players, for instance to model players located at different distance of the gateway, and we can also consider networks with some ``jammers'' whose purpose is not to communicate to the gateway in a collaborative way, like the $M$ devices, but to interfere with the communications of the $M$ devices.

@@

In the model we presented above, we assumed the number of players $M$ to be fixed in time during the learning process.
Without removing this hypothesis (we study this case below in Section~\ref{sub:5:arrivalDepartures}), it is interesting to remark that we made no hypothesis on whether the players can known this value $M$ or not.
Our proposals, \RandTopM{} and \MCTopM, both assume to know $M$ beforehand, like it was done for our main inspiration \RhoRand.

\paragraph{Performance of our proposals for a wrong value of $M$?}
\label{par:5:usingWrongValueofM}
%
We can start by asking whether our most efficient proposal, \MCTopM-\klUCB, is still efficient if it uses a value $M'$ different than the real number of players $M$.
Even though we did not include numerical simulations for this case in Section~\ref{sec:5:experiments} above, we did some tests, which confirmed two disappointing results that were also proved analytically.
First, the three algorithms (\RhoRand, \RandTopM{} and \MCTopM) give linear regret if they are using a value $M'$ strictly smaller than $M$ (and if $\mu^*_{M-1} > \mu^*_M$), as players will converge to play about $T-\bigO{\log(T)}$ times the $M-1$ best arms, leading to at least one collision most of the time, and thus a linear regret.
Second, if the $M$ players falsely use a value $M' > M$, then there is also a certain (fixed) probability to achieve a linear regret. Indeed, imagine one player ($M=1$) running \MCTopM{} with the false knowledge of $M'=2$, and if it learned to accurately identify the set of the $2$ best arms, then the \MCTopM{} orthogonalization scheme can make it play the worst of the two arms, and as $M=1$ this player will never encounter any collision, thus playing this suboptimal arm for about $T-\bigO{\log(T)}$ times, also leading to linear regret.

@@

Similarly to what was proposed for the \rhoRandEst{} algorithm in \cite{Anandkumar11}, we could have worked on proposing and analyzing an extension of our proposals that could efficiently learn the value of $M$ the number of player.
We implemented this \rhoRandEst{} policy in our library SMPyBandits \cite{SMPyBandits}, as well as this mechanism for our proposals \RandTopM{} and \MCTopM.
Building from the theoretical analysis given for \rhoRandEst{} in \cite{Anandkumar11}, and our analysis of \MCTopM-\klUCB, we believe it is possible to show that the aforementioned extension of our proposal also achieves sub-linear regret without requiring players to know $M$ in the beginning of the bandit game.
More precisely, we believe that \MCTopM-\klUCB{} can still give order-optimal logarithmic regret if $M$ players use it, and this extension of Theorem~\ref{thm:5:LogarithmicRegret_MCTopMklUCB} is not included due to space constraints.
Writing its proof and performing more simulations are left as possible future work.

@@

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar increase on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $\times 3.4$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\cO(1)$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected, and much worse than \MCTopM.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of our proposal \MCTopM-\klUCB.

@@

As reminded above, our model assumes the number of players $M$ remain fixed during all the bandit game.
However, in real-world wireless networks, when players model communicating devices connected to a single gateway, devices can arrive or leave the network at any time.
The existing previous work on multi-player bandit models are all motivated by possible applications to wireless networks, but most of them assume $M$ to be fixed.
The first work studying the relaxation of this hypothesis is \cite{Rosenski16}, where this case is called the ``dynamic setting''.
If the arrival or departures of players is not random, but determined in advance while still being unknown to any player, the natural notion of regret is the following, where the expectancy $\E[\bullet]$ is capturing the randomness in the sensing information, as well as in the players' decisions (\ie, collisions):
\begin{equation}\label{eq:5:defRegretDynamicSetting}
    R_T^{\text{dyn}} = \sum_{t=1}^T \sum_{k=1}^{M(t)} \mu^*_{k} - \E\Bigl[ \sum_{t=1}^T \sum_{j=1}^{M(t)} r^j(t) \Bigr].
\end{equation}

@@

In \cite{Rosenski16}, it is assumed that the players all know a lower-bound $L$ on the length of all the intervals during which arrival or departures of players are allowed.
A naive idea, if $L$ is large enough, is simply to restart the underlying algorithm every $L$ time steps, in order to directly benefit from the theoretical guarantees of the ``static setting'' (where $M$ stays constant).
However, this idea yields a large regret if the length of ``static'' intervals $L$ is too small.
Applied to the \MusicalChair{} algorithm, the authors in \cite{Rosenski16} call this basic extension Dynamic \MusicalChair
Under the simple hypothesis that the overall number of players entering and leaving the game is sub-linear in $T$ (\ie, a $\smallO{T}$), they analyze the regret of Dynamic \MusicalChair{} and prove it is also sub-linear (see Theorem~2 in Section~3.4).
%
Under the same hypothesis, and if the lower-bound $L$ is known before-hand and is large enough, then we could also apply the same idea as from \cite{Rosenski16} to our approach. We believe that we could easily prove that a sub-linear regret is achievable, if all players run \MCTopM-\klUCB{} (and if currently active players restart their memory of the past observations every $L$ time steps).
As the regret guarantees are stronger (\ie, smaller regret upper-bound) for \MCTopM{} than \MusicalChair, we also believe that in this ``slowly varying'' dynamic setting, applying the idea of Dynamic \MusicalChair{} from \cite{Rosenski16} to our proposal \MCTopM{} would also give a small regret upper-bound.

@@

We presented in Section~\ref{sec:5:model} the model \modeltrois, without sensing information. Players can only observe $Y_k(t)$, the product of the \iid{} random sensing information from arm $k$ and of the no-collision indicator.
This model seems harder than the model with sensing information, and even though our proposal \Selfish{} works fine in simulations (in terms of average regret), we proved that it can yield linear regret.
In our paper \cite{Besson2018ALT} as well as the previous sections, it was left as a future work to know if an algorithm can achieve sub-linear regret in this harder model without sensing information.

Inspired by our article \cite{Besson2018ALT},
Boursier and Perchet studied this question in the summer $2018$ following its publication \cite{BoursierPerchet18}.
Their answer is that the model without sensing information is essentially not harder than the model with sensing information.
%
Similarly, Lugosi and Mehrabian studied the same problem \cite{LugosiMehrabian18}.
In both works, the authors detail algorithms that give in both cases a logarithmic regret if $M \leq K$ players all independently implement the proposed algorithm.

@@

The results presented in \cite{LugosiMehrabian18} are based on some hypotheses, for instance the tuning they propose for the length $g$ of the uniform exploration phase in the beginning of their ``Musical Chair''-like algorithm is based on a prior knowledge of the horizon $T$.
In Section~4 they explain how to relax the assumptions of their results.
For the same example, the ``doubling trick'' technique can be used to obtain a regret upper bound for an algorithm unaware of the value of $T$, within a constant multiplicative factor of the upper bound given for the algorithm aware of $T$ (Section~4.1). Because the regret bound is of the form $\bigO{\sqrt{T} \log(T)}$, a simple ``doubling trick'' of increasing horizons of lengths $T_i = 2^i$ works well, as proposed in \cite{CesaLugosi06} and as studied in depth in our article \cite{Besson2018DoublingTricks}, and quickly presented in Appendix~\ref{app:2:DoublingTricks}.
%
They also study in Section~4.3 an extension of the model for the case with more players than arms, but we do not give more details on this aspect. Their definition of a centralized regret for this case is an interesting and natural generalization of our definition, and they also proposed an algorithm achieving $\bigO{M K \log(T) \exp(4M/K) / \Delta^2}$ regret in this case.
Finally, they also proposed in Section~4.4 an extension of their algorithm to estimate the number of players $M$, which is analyzed as for the Musical Chair algorithm in \cite{Rosenski16}, and also achieve logarithmic regret.
Note that it is significantly harder to estimate $M$ without collision information, and Algorithm~3 in page 24 is quite complex.
We did not implement it, and it would be interesting to run some numerical simulations in order to validate it empirically.

@@

Finally, the very recent work of \cite{Zafaruddin2019} is the first one to present experiments of reinforcement learning done on simulated LTE and 5G channels.
The mathematics behind their model are actually quite close to our model, but they explain it in terms of OFDMA and Quality-of-Service (QoS).
Their algorithm is essentially based on a pre-agreement of the $M$ players, that will deterministically run an alternance of exploration phase, auction phase and exploitation phase, of (exponentially) increasing durations.
By diving into the details of the modulation and giving explicitly the form of the uplink messages sent by the devices, the authors are able to set-up two different uplink packets, to efficiently perform the auction phase (see Figure~2).
They prove a regret upper-bound of the order $R_T = \bigO{\log(T)}$, with no special care regarding the constants, but we can also note that their algorithm require a prior knowledge of $\Delta_{\min}$ a problem-dependent constant (Theorem~3).

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focussed on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $\{1,\dots,M\}$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn\footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.}, where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
The first \rhoLearn uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multi-play version of \klUCB{} and our proposal \MCTopM-\klUCB{} for comparison.

@@

% FIXME much more details?
Other works in the same line of research included \cite{modiDemo2016} implemented using the same USRP testbed as for our demonstration in Chapter~\ref{chapter:4} (Section~\ref{sec:4:gnuradio}),
and the first work of a research team based in IIT Dehli, \cite{kumar2016two}.
%
More recent works by the same team, \cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}, all follow the same approach and include an experimental section that shows the results of an implementation of the proposed algorithms on USRP boards.
\TODOL{I should explain more, no? Who does what and why? So long...}

@@

On the first hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in\{1,\dots,M\}$ knows its ID $j$ (see above the discussion we give on this unrealistic assumption).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our proposals \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches our conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in\{1,\dots,M\}$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.

>>>>

In this Chapter~\ref{chapter:5}, we are interested in a more formal approach to the decentralized learning problem presented in Chapter~\ref{chapter:4}.
We restrict to the easier case of at most $M \leq K$ devices in a network with $K$ channels, because it was found very hard to analyze the aforementioned IoT network model.
%
We start by reviewing previous works on multi-player MAB models, which all considered the easier case of \emph{sensing feedback}.

For this first model, we present two algorithms, \RandTopM{} and \MCTopM, based on the combination of an efficient MAB index policy (we chose \klUCB) and a smart orthogonalization procedure, based on a random hoping procedure called Musical Chair.
Like in previous works, we consider the centralized system regret (multi-player regret).
We start by showing an improved asymptotical regret lower-bound for any algorithm of a certain class, including previous solutions such as \rhoRand{} and our two solutions.
We then analyze the \MCTopM{} algorithm and we show that its regret upper-bound is logarithmic and order-optimal, improving over the previous state-of-the-art.
%  with a regret bounded by $\bigO{\log(T)}$ for a game at horizon $T$.
We also present extensive numerical simulations that show that our proposal outperforms all previous solutions and is much more efficient in this easier model of sensing feedback with a fixed and known number of players $M \leq K$ accessing $K$ channels.

@@

Finally, we review other extensions of the models, and give a overview of the current state-of-the-art.
For some extensions, we discuss how to adapt our proposals and illustrate the empirical performances of such modification of \MCTopM-\klUCB{}, leaving theoretical analyses as future works.

@@

\newpage  % WARNING
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\section{Literature review of many extensions of the models}
\label{sec:5:literatureReviewOtherModels}
% ----------------------------------------------------------------------------

@@

Many extensions of the simpler model of multi-player bandits have been considered.
The number of players $M$ can be fixed but initially unknown to the players, the sensing information can be absent (like the model \modeltrois{} presented above), there could be communications between players (happening at each time step or only occasionally), or $M$ could evolve over time to model the possibility of arrivals or departures of players (\ie, connexions and disconnections of devices in a wireless networks).
Also inspired by real-world wireless networks, the arm means may vary among players, for instance to model players located at different distance of the gateway, and we can also consider networks with some ``jammers'' whose purpose is not to communicate to the gateway in a collaborative way, like the $M$ devices, but to interfere with the communications of the $M$ devices.

@@

In the model we presented above, we assumed the number of players $M$ to be fixed in time during the learning process.
Without removing this hypothesis (we study this case below in Section~\ref{sub:5:arrivalDepartures}), it is interesting to remark that we made no hypothesis on whether the players can known this value $M$ or not.
Our proposals, \RandTopM{} and \MCTopM, both assume to know $M$ beforehand, like it was done for their main inspiration, \RhoRand.

\paragraph{Performance of our proposals for a wrong value of $M$?}
\label{par:5:usingWrongValueofM}
%
We can start by asking whether the most efficient algorithm, \MCTopM-\klUCB, is still efficient if it uses a value $M'$ different than the real number of players $M$.
Even though we did not include numerical simulations for this case in Section~\ref{sec:5:experiments} above, we did some tests, which confirmed two disappointing results that were also proved analytically.
First, the three algorithms (\RhoRand, \RandTopM{} and \MCTopM) give linear regret if they are using a value $M'$ strictly smaller than $M$ (and if $\mu^*_{M-1} > \mu^*_M$), as players will converge to play about $T-\bigO{\log(T)}$ times the $M-1$ best arms, leading to at least one collision most of the time, and thus a linear regret.
Second, if the $M$ players falsely use a value $M' > M$, then there is also a certain (fixed) probability to achieve a linear regret. Indeed, imagine one player ($M=1$) running \MCTopM{} with the false knowledge of $M'=2$, and if it learned to accurately identify the set of the $2$ best arms, then the \MCTopM{} orthogonalization scheme can make it play the worst of the two arms, and as $M=1$ this player will never encounter any collision, thus playing this suboptimal arm for about $T-\bigO{\log(T)}$ times, also leading to linear regret.

@@

Similarly to what was proposed for the \rhoRandEst{} algorithm in \cite{Anandkumar11}, we could have worked on proposing and analyzing an extension of our proposals that could efficiently learn the value of $M$ the number of player.
We implemented this \rhoRandEst{} policy in our library SMPyBandits \cite{SMPyBandits}, as well as this mechanism for \RandTopM{} and \MCTopM.
Building from the theoretical analysis given for \rhoRandEst{} in \cite{Anandkumar11}, and the analysis of \MCTopM-\klUCB, we believe it is possible to show that the aforementioned extension also achieves sub-linear regret without requiring players to know $M$ in the beginning of the bandit game.
More precisely, we believe that \MCTopM-\klUCB{} can still give order-optimal logarithmic regret if $M$ players use it, and this extension of Theorem~\ref{thm:5:LogarithmicRegret_MCTopMklUCB} is not included due to space constraints.
Writing its proof and performing more simulations are left as possible future work.

@@

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar increase on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $\times 3.4$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\cO(1)$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected, and much worse than \MCTopM.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of \MCTopM-\klUCB.

@@

As reminded above, the model assumes the number of players $M$ remain fixed during all the bandit game.
However, in real-world wireless networks, when players model communicating devices connected to a single gateway, devices can arrive or leave the network at any time.
The existing previous work on multi-player bandit models are all motivated by possible applications to wireless networks, but most of them assume $M$ to be fixed.
The first work studying the relaxation of this hypothesis is \cite{Rosenski16}, where this case is called the ``dynamic setting''.
If the arrival or departures of players is not random, but determined in advance while still being unknown to any player, the natural notion of regret is the following, where the expectancy $\E[\bullet]$ is capturing the randomness in the sensing information, as well as in the players' decisions (\ie, collisions):
\begin{equation}\label{eq:5:defRegretDynamicSetting}
    R_T^{\text{dyn}} = \sum_{t=1}^T \sum_{k=1}^{M(t)} \mu^*_{k} - \E\Bigl[ \sum_{t=1}^T \sum_{j=1}^{M(t)} r^j(t) \Bigr].
\end{equation}

@@

In \cite{Rosenski16}, it is assumed that the players all know a lower-bound $L$ on the length of all the intervals during which arrival or departures of players are allowed.
A naive idea, if $L$ is large enough, is simply to restart the underlying algorithm every $L$ time steps, in order to directly benefit from the theoretical guarantees of the ``static setting'' (where $M$ stays constant).
However, this idea yields a large regret if the length of ``static'' intervals $L$ is too small.
Applied to the \MusicalChair{} algorithm, the authors in \cite{Rosenski16} call this basic extension Dynamic \MusicalChair
Under the simple hypothesis that the overall number of players entering and leaving the game is sub-linear in $T$ (\ie, a $\smallO{T}$), they analyze the regret of Dynamic \MusicalChair{} and prove it is also sub-linear (see Theorem~2 in Section~3.4).
%
Under the same hypothesis, and if the lower-bound $L$ is known before-hand and is large enough, then we could also apply the same idea as from \cite{Rosenski16} to our approach. We believe that we could easily prove that a sub-linear regret is achievable, if all players run \MCTopM-\klUCB{} (and if currently active players restart their memory of the past observations every $L$ time steps).
As the regret guarantees are stronger (\ie, smaller regret upper-bound) for \MCTopM{} than \MusicalChair, we also believe that in this ``slowly varying'' dynamic setting, applying the idea of Dynamic \MusicalChair{} from \cite{Rosenski16} to \MCTopM{} would also give a small regret upper-bound.

@@

We presented in Section~\ref{sec:5:model} the model \modeltrois, without sensing information. Players can only observe $Y_k(t)$, the product of the \iid{} random sensing information from arm $k$ and of the no-collision indicator.
This model seems harder than the model with sensing information, and even though the proposal \Selfish{} works fine in simulations (in terms of average regret), we proved that it can yield linear regret.
In our paper \cite{Besson2018ALT} as well as the previous sections, it was left as a future work to know if an algorithm can achieve sub-linear regret in this harder model without sensing information.

Inspired by \cite{Besson2018ALT},
Boursier and Perchet studied this question in the summer $2018$ following its publication \cite{BoursierPerchet18}.
Their answer is that the model without sensing information is essentially not harder than the model with sensing information.
%
Similarly, Lugosi and Mehrabian studied the same problem \cite{LugosiMehrabian18}.
In both works, the authors detail algorithms that give in both cases a logarithmic regret if $M \leq K$ players all independently implement the proposed algorithm.

@@

The results presented in \cite{LugosiMehrabian18} are based on some hypotheses, for instance the tuning they propose for the length $g$ of the uniform exploration phase in the beginning of their ``Musical Chair''-like algorithm is based on a prior knowledge of the horizon $T$.
In Section~4 they explain how to relax the assumptions of their results.
For the same example, the ``doubling trick'' technique can be used to obtain a regret upper bound for an algorithm unaware of the value of $T$, within a constant multiplicative factor of the upper bound given for the algorithm aware of $T$ (Section~4.1). Because the regret bound is of the form $\bigO{\sqrt{T} \log(T)}$, a simple ``doubling trick'' of increasing horizons of lengths $T_i = 2^i$ works well, as proposed in \cite{CesaLugosi06} and as studied in depth in our article \cite{Besson2018DoublingTricks}, and quickly presented in Appendix~\ref{app:2:DoublingTricks}.
%
They also study in Section~4.3 an extension of the model for the case with more players than arms, but we do not give more details on this aspect. Their definition of a centralized regret for this case is an interesting and natural generalization of the definition, and they also proposed an algorithm achieving $\bigO{M K \log(T) \exp(4M/K) / \Delta^2}$ regret in this case.
Finally, they also proposed in Section~4.4 an extension of their algorithm to estimate the number of players $M$, which is analyzed as for the Musical Chair algorithm in \cite{Rosenski16}, and also achieve logarithmic regret.
Note that it is significantly harder to estimate $M$ without collision information, and Algorithm~3 in page 24 is quite complex.
We did not implement it, and it would be interesting to run some numerical simulations in order to validate it empirically.

@@

Finally, the very recent work of \cite{Zafaruddin2019} is the first one to present experiments of reinforcement learning done on simulated LTE and 5G channels.
The mathematics behind their model are actually quite close to the model, but they explain it in terms of OFDMA and Quality-of-Service (QoS).
Their algorithm is essentially based on a pre-agreement of the $M$ players, that will deterministically run an alternance of exploration phase, auction phase and exploitation phase, of (exponentially) increasing durations.
By diving into the details of the modulation and giving explicitly the form of the uplink messages sent by the devices, the authors are able to set-up two different uplink packets, to efficiently perform the auction phase (see Figure~2).
They prove a regret upper-bound of the order $R_T = \bigO{\log(T)}$, with no special care regarding the constants, but we can also note that their algorithm require a prior knowledge of $\Delta_{\min}$ a problem-dependent constant (Theorem~3).

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focussed on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $\{1,\dots,M\}$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn\footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.}, where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
The first \rhoLearn uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multi-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.

@@

% FIXME much more details?
Other works in the same line of research included \cite{modiDemo2016} implemented using the same USRP testbed as for our demonstration in Chapter~\ref{chapter:4} (Section~\ref{sec:4:gnuradio}),
and the first work of a research team based in IIT Dehli, \cite{kumar2016two}.
%
More recent works by the same team, \cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}, all follow the same approach and include an experimental section that shows the results of an implementation of the proposed algorithms on USRP boards.
% \TODOL{I should explain more, no? Who does what and why? So long...}

@@

On the first hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in\{1,\dots,M\}$ knows its ID $j$ (see above the discussion we give on this unrealistic assumption).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our algorithm \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches the conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in\{1,\dots,M\}$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.
